plots with prolactin

### 2019-12-31 analysis/16_PRL.Rmd
now with prolactin candidate plot

@@

@@

@@

## prolactin manip

@@

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird
candidates.pit$X1 <- candidates.pit$V1
geneshormones <- left_join(candidates.pit, hormones) %>%
  select(-X1, -V1, -okay, - icons, -music, -iconpath) %>%
  drop_na()

(geneshormones$bird_id)
(hormones$bird_id)

@@

@@

p8 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "PRL", subtitle = "Pituitary") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5)   +
  geom_hline(yintercept=17) +
  geom_hline(yintercept=18) +
  geom_hline(yintercept=19) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=21)

@@

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
write.csv(aov_all, "../results/16_aov_PRLsex.csv")
write.csv(aov_manip, "../results/16_aov_PRLsextreatment.csv")

@@

>>>>

# Plots with Prolactin

@@

## Circulating levels of prolactin

@@

## Prolactin (_PRL_) and _BRCA1_ expression in the pituitary

@@

## Manipulation of parental care and _PRL_ and _BRCA1_ expression

@@

## Genes an hormones (in progress, don't have all the bird ids lining up.)

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird
candidates.pit$X1 <- candidates.pit$V1

geneshormones <- left_join(candidates.pit, hormones) %>%
  select(-X1, -V1, -okay, - icons, -music, -iconpath) %>%
  drop_na()

head(geneshormones$bird_id)
head(hormones$bird_id)

@@

## Prolactin hormone statistics

@@

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1))  %>%
  dplyr::filter(treatment %in% charlevels)
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = charlevels)

p8 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "PRL", subtitle = "Pituitary") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5)   +
  geom_hline(yintercept=17) +
  geom_hline(yintercept=18) +
  geom_hline(yintercept=19) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=21) +
  theme(axis.title.y  = element_text(face = "italic"))

@@

## WGCNA candidates

```{r WGCNAcandidates}

#WGCNAgenes <- read_csv("../results/08_PRL_associated.csv") %>% pull(x)
#WGCNAgenes <- c("FBXO5", "NUF2", "PTTG1", "BUB1", "PRL", "ASPM", "AURKA", "CDC20", "NEK2", "CKS2", 
#                  "MYC", "CCNB3", "FANCC", "STC1", "RACGAP1", "E2F7", "PLK1", "EXO1", "CENPI", "CDK1")
WGCNAgenes <- c("PRL", "PAX7", "ASPM", "AURKA",  "CDC20", "CENPF", "MYC",  "CDK1", "LBH", "BRCA1", "FOXM1", "FBXO5")

WGCNAgenes.pit <- vsd.pit %>% dplyr::filter(genes %in% WGCNAgenes)
WGCNAgenes.pit <- as.data.frame(WGCNAgenes.pit)
row.names(WGCNAgenes.pit) <- WGCNAgenes.pit$genes
WGCNAgenes.pit <- pivot_longer(WGCNAgenes.pit, -genes, names_to = "V1", values_to = "expression")
head(WGCNAgenes.pit)
WGCNAgenes.pit <- left_join(colData.pit, WGCNAgenes.pit) %>%
  filter(study == "charcterization")
WGCNAgenes.pit$treatment <- factor(WGCNAgenes.pit$treatment, levels = alllevels)

WGCNAgenes.pit$genes <- factor(WGCNAgenes.pit$genes)
WGCNAgenes.pit$genesnum <- round(as.numeric(WGCNAgenes.pit$genes), digits = -1)

p1 <- ggplot(WGCNAgenes.pit, aes(x = treatment, y = expression)) +
  geom_boxplot(aes(fill = treatment)) +
  facet_wrap(~genes, scales = "free_y") +
  theme_B3() +
  theme(legend.position = "none") +
  #scale_color_manual(values = sexcolors) +
  theme(axis.text.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_blank(),
        strip.text = element_text(face = "italic")) +
  labs( x = "parental stage", y = "pituitary expression",
        subtitle = "Genes that are coexpressed with prolactin and regulate development")
p1

@@

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
write.csv(aov_all, "../results/16_aov_PRLsex.csv")
write.csv(aov_manip, "../results/16_aov_PRLsextreatment.csv")
```
